\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
executive summary and other sections

@@

@@

This was our first time trying the AR image recognition on the actual signs
at Kinkaku-ji, rather than photographs of the signs, and it worked quite
well. Vuforia was able to recognize almost all of the signs, even in
different lighting than when the reference images were taken. For image
targets that were small, far away, or obscured by shadows image recognition
was slower, but Vuforia was always able to recognize them eventually. We
discovered that the targets that worked best were large, had a lot of
high-contrast text, and were uniformly lit.

@@

\section{Pivots}
\label{sec:pivots}

Throughout the duration of the project, the goalposts shifted multiple times.
This section details some of the initial plans that fell through.

@@

One idea that was proposed initially was an AR audio experience using 3D
spatialized audio.

>>>>

We built, tested and polished a mobile app to deliver an audio tour,
incorporating various AR features to enhance the experience. In this app, which
we call ARuko, many of the AR features were aimed at improving accessibility.
These features included translating signs and providing additional info on the
physical map located at the site. Other features were purely for spectacle,
such as the ability to take an AR `souvenir' home by pointing the camera at the
ticket.

ARuko went through multiple iterations of user testing and bug testing at the
site of the audio tour, Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's and
functionality was dictated by Atticus Sims of Kyoto VR, who plans to monetize
the app. We also worked closely with the IQP team, who has been tasked with
exploring funding options and creating promotional content.

Since our app had to deliver an audio tour supplemented by images based on your
GPS position, we developed an internal tool to design these regions. Editour
provides a rich editing suite for designing tours with images and audio.
Section~\ref{sec:editingATour} goes into detail about the features of this web
app. We also wrote a backend to manage the tour files, allowing one of us (or
our sponsor, Atticus Sims) to download a zip file containing all of the media
and info to reconstruct the tour. This zip can be extracted into the Unity
project, which reconstructs the tour from the downloaded contents. We were able
to host the backend on the server provided by Kyoto VR's hosting plan; we
discuss the hurdles that we overcame to deploy the Editour backend with Kyoto
VR's current setup in Section~\ref{sec:deployingTheEditourBackend}.

At the end of this paper, we also discuss the alternative AR app concepts that
were explored before development became completely focused on the tour app
ARuko.

@@

\subsubsection{Map Overlay Feature}
\label{sec:mapOverlayFeature}

Near the entrance of Kinkaku-ji before the ticket gate, there is a large
illustrated map. Much like the signage, there is no language on the map other
than Japanese. Using the AR camera within the app, you can project information
onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
the walking tour, including a few translated labels.

\begin{figure}[h] \centering
    \includegraphics[width=0.3\textwidth]{ar-map-feature.png}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:arMapFeature}
\end{figure}

@@

This was our first time trying the AR image recognition on the actual signs at
Kinkaku-ji, rather than photographs of the signs, and it worked surprisingly
well. Vuforia was able to recognize almost all of the signs, even in different
lighting than when the reference images were taken. For image targets that were
small, far away, or obscured by shadows image recognition was slower, but
Vuforia was always able to recognize them eventually. We discovered that the
targets that worked best were large, had a lot of high-contrast text, and were
uniformly lit.

@@

\section{Alternative AR App Concepts}
\label{sec:alternativeArAppConcepts}

Throughout the duration of the project, the goalposts shifted multiple times.
This section details some of the initial plans that we explored before Atticus
shifted our focus to a walking tour app with AR features.

@@

One idea that was proposed initially was an AR audio experience using 3D
spatialized audio. Instead of traditional AR where the user is constantly
looking through the camera, this experience would allow users to keep their
phones in their pockets while taking the tour. Sound sources would change in
physically based ways using motion tracking.

We spent the second and third week creating demos to explore the possibility of
a 3D spatialized audio tour. We found that this would be very difficult to do
without the use of the camera. All of the technology for mobile AR we explored
in Section~\ref{sec:platforms} depended heavily on the camera. If we were to
build a 3D spatialized audio tour that ran entirely without use of the camera,
we would not be able to take advantage of any of the useful features of the AR
libraries we explored. Furthermore, Unity would be relegated to the simple role
of exporting our app to multiple devices; we would not have any need to take
advantage of its 3D capabilities.

Thusly, we decided to see what was possible using the camera instead. We were
able to get sound sources to fade in and out based on the distance to an image
target. Naturally, if the image target were to go out of view of the camera,
Vuforia stopped trying to estimate the camera's distance to the last known
location of the image target. In order to make this work in the way Atticus
imagined, we would need a way to shift to our own method of estimating distance
to the sound source once the image target had been lost. While this might have
been possible, it was difficult to estimate the amount of effort this would
take, since we would essentially be implementing a feature seemingly not
supported by current AR libraries.

We explained the technical hurdles of this concept to Atticus. Ultimately, our
focus shifted away from this idea for other logistical reasons. Initially,
Atticus introduced the possibility of working closely with Kishi Bashi or
Yannick Paget to produce the soundscape for the 3D spatialized audio tour.
Yannick Paget is a French musician that became established in Japan. He is both
conductor and composer, originally trained as a professional pianist and
percussionist. He has written music for theater, film and orchestras around the
world. Many of his original compositions were inspired by his experience living
in Japan, such as Tears of Sakura
(\begin{CJK}{UTF8}{min}サクラの涙\end{CJK})~\autocite{yannickpaget2016}. Kishi
Bashi was born in Seattle and grew up in Virginia. Kishi Bashi has appeared at
many major music festivals, toured the US extensively, and has even released
his own line of coffee! His latest album, Omoiyari, was released on May
31\textsuperscript{st}, 2019~\autocite{kishibashi2019}.

\subsection{AR Art Gallery}
\label{sec:arArtGallery}

Atticus Sims proposed the idea of working with Michael Whittle. Michael Whittle
received his PhD at the Kyoto City University of Arts in 2014. His art has
appeared in dozens of solo exhibitions and group exhibitions across the world,
including Kyoto, Beijing, London and New York~\autocite{michaelwhittle2019}.
Kyoto VR has worked with Michael Whittle in the past to create a 3D scan of a
solo exhibition, `Portraits of Thought'. This exhibition displayed diagrams
inspired by real science and mathematics. Atticus provided us with some
diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
to know how well certain pieces of art would work as AR image targets. All of
images that were provided to us were ranked as ``five stars'' by Vuforia,
indicating that those images would serve well as AR image targets.

\begin{figure}[h]
	\centering
	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
    \caption{A screenshot of the 3D scan of `Portraits of Thought,' accessible
    from the web}
	\label{fig:exhibitionScan}
\end{figure}
